\subsection{RQ2: switching occurs outside the profit gate}\label{subsec:results_switching}

The primary five-percent profit gate is inactive for 6,360 of the 8,461 complete direct-comparison issuer-years. Table~\ref{tab:inference_switching} shows that 8.0 percent of observations switch non-zero CFO sign, 20.5 percent cross a common fiscal-year CFO-quintile boundary, and 5.1 percent switch high-$|TA|$ membership. Among switchers, 61.7, 65.8, and 59.0 percent, respectively, are outside the profit gate. All three issuer-cluster lower confidence bounds exceed one half. The switches are not numerically trivial: the median CFO difference among sign switchers is 8.8 percent of beginning assets and its ninetieth percentile is 40.0 percent; high-$|TA|$ switchers have a median absolute-membership-distance measure of 19.1 percent of assets.

\begin{table}[htbp]
\centering
\caption{Direct reporting-state switching and profit-gate coverage}
\label{tab:inference_switching}
\scriptsize
\resizebox{\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
Outcome & $N$ & Switches & Switch rate [95\% CI] & Outside-gate share [95\% CI] & Median magnitude & P90 magnitude \\
\midrule
CFO sign & 8,461 & 681 & 8.05\% [7.30, 8.82] & 61.67\% [57.43, 65.90] & 0.088 & 0.400 \\
Common-boundary CFO category & 8,461 & 1,734 & 20.49\% [19.22, 21.78] & 65.80\% [63.01, 68.51] & 1 category & 3 categories \\
High $|TA|$ & 8,461 & 434 & 5.13\% [4.48, 5.80] & 58.99\% [53.55, 64.69] & 0.191 & 0.579 \\
\bottomrule
\end{tabular}%
}
\begin{minipage}{0.97\textwidth}\footnotesize
\textit{Notes:} The direct switching sample requires finite PAT, CFO, total-accrual, and beginning-asset values in both states. A CFO-sign switch requires both state values to have opposite signs. CFO categories use post-audit-state fiscal-year quintile boundaries applied to both states. High-$|TA|$ uses the post-audit-state fiscal-year ninetieth percentile. Intervals are 2,000-draw issuer-cluster bootstrap percentile intervals.
\end{minipage}
\end{table}

Model-based switching is similarly stable across specifications (Table~\ref{tab:da_switching}). Under the pooled post-audit-reference benchmark, DA-sign switching ranges from 10.4 to 10.8 percent and high-$|DA|$ switching from 4.9 to 5.1 percent. Between 61.6 and 64.5 percent of DA-sign switches and between 59.2 and 60.3 percent of high-$|DA|$ switches lie outside the profit gate. Pooled high-$|DA|$ Jaccard overlap ranges from 0.617 to 0.632, with year-specific values spanning 0.534 to 0.704. The median common-CDF percentile displacement is 2.3--2.5 percentile points, whereas the ninetieth percentile is approximately 31 points. Central rank movement is therefore modest, but the upper tail experiences substantial reordering.

\begin{table}[htbp]
\centering
\caption{Discretionary-accrual switching across model families}
\label{tab:da_switching}
\scriptsize
\resizebox{\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
Model & $N$ & DA-sign switch [95\% CI] & Sign switches outside gate [95\% CI] & High-$|DA|$ switch & High-$|DA|$ outside gate & Jaccard \\
\midrule
Jones & 7,801 & 10.51\% [9.63, 11.40] & 62.44\% [58.75, 66.22] & 4.94\% & 59.22\% & 0.632 \\
Modified Jones & 7,801 & 10.45\% [9.57, 11.34] & 64.54\% [60.62, 68.57] & 4.95\% & 59.59\% & 0.628 \\
Kothari-style ROA-adjusted & 7,801 & 10.82\% [9.93, 11.76] & 61.61\% [57.69, 65.30] & 5.13\% & 59.75\% & 0.617 \\
Nonlinear modified Jones & 7,801 & 10.78\% [9.90, 11.70] & 61.71\% [57.58, 65.75] & 5.10\% & 60.30\% & 0.617 \\
\bottomrule
\end{tabular}%
}
\begin{minipage}{0.97\textwidth}\footnotesize
\textit{Notes:} Results use pooled historical models and the post-audit-reference benchmark. High-$|DA|$ uses a common post-audit-state fiscal-year ninetieth-percentile boundary. Jaccard overlap is calculated from pooled eligible memberships.
\end{minipage}
\end{table}

Table~\ref{tab:switch_benchmarks} compares observed sign switching with two state-independent benchmarks. CFO-sign switching exceeds the symmetric-sign 97.5th percentile but is below the within-year signed-shift-reassignment distribution. In contrast, all four DA-sign rates exceed the 97.5th percentile of both benchmarks. Thus, CFO switching is unusually high relative to neutral directions assigned to the observed shift magnitudes, but not relative to the within-year distribution of observed signed CFO shifts. DA switching remains unusually high under both comparisons.

\begin{table}[htbp]
\centering
\caption{State-independent sign-switch benchmarks for RQ2}
\label{tab:switch_benchmarks}
\scriptsize
\resizebox{\textwidth}{!}{%
\begin{tabular}{llrrr}
\toprule
Outcome & Model & Observed & Symmetric-sign mean [95\% interval] & Signed-shift reassignment mean [95\% interval] \\
\midrule
CFO sign & Direct & 8.05\% & 6.65\% [6.28, 7.04] & 10.18\% [9.66, 10.73] \\
DA sign & Jones & 10.51\% & 8.21\% [7.75, 8.66] & 9.27\% [8.74, 9.83] \\
DA sign & Modified Jones & 10.44\% & 8.15\% [7.71, 8.60] & 9.21\% [8.70, 9.74] \\
DA sign & Kothari-style ROA-adjusted & 10.82\% & 8.23\% [7.80, 8.68] & 9.33\% [8.77, 9.86] \\
DA sign & Nonlinear modified Jones & 10.78\% & 8.10\% [7.63, 8.55] & 9.26\% [8.69, 9.79] \\
\bottomrule
\end{tabular}%
}
\begin{minipage}{0.97\textwidth}\footnotesize
\textit{Notes:} Each benchmark uses 2,000 draws. Signed shifts are reassigned within fiscal-year cells and, for DA, within model--reference-benchmark--fiscal-year cells. For the symmetric-sign benchmark, all one-sided Monte Carlo probabilities are below 0.001. Under signed-shift reassignment, the CFO probability equals 1.000 and every DA probability is below 0.001.
\end{minipage}
\end{table}

Coverage depends on how narrowly the profit gate is defined. When the numerical threshold is reduced from 5.0 to 2.5 percent, the outside-gate shares fall to 48.8 percent for CFO sign, 54.1 percent for CFO category, and 49.8 percent for high-$|TA|$; the intersection--union coverage rule therefore fails at the narrower threshold. At 5.0 percent, the corresponding shares are 61.7, 65.8, and 59.0 percent. They rise further at the 7.5- and 10-percent thresholds. The evidence therefore supports incomplete coverage by the prespecified five-percent gate, not by every possible profit-change convention.
