\section{Results}\label{sec:results}

\subsection{Analysis population and direct reporting-state differences}\label{subsec:results_sample}

The locked nonfinancial panel contains 8,584 issuer-years with both constructed pre-audit and post-audit annual states. Of these, 8,461 have finite profit, CFO, total-accrual, and beginning-asset measures for the direct comparisons. The pooled post-audit-reference accrual models produce 7,803 finite DA cases. Of these, 7,801 also have the complete PAT, CFO, and profit-gate information required for the RQ1 attribution and RQ2 coverage analyses. The two-observation difference therefore arises only at the component and gate-merging layers. The historical estimation window begins in 2016, so 2016 provides no prior audited training observations under the locked design. The first estimable test year is therefore 2017, and all model results cover 2017--2025 using audited observations strictly preceding each test year.

The execution audit confirms that the reported bundle follows the final method contract. All Jones-family regressions omit an ordinary intercept, predictors are rescaled without mean centring, and inverse beginning assets remain an explicit regressor. The attribution is the exact three-player Shapley allocation across PAT movement, CFO movement, and the residual benchmark component. Signed-shift reassignment is performed within fiscal-year cells. The maximum observed Shapley reconstruction error is $2.11\times10^{-15}$.

Table~\ref{tab:descriptive_statistics} shows that direct reporting-state differences are concentrated in CFO rather than profit. The median absolute CFO difference is 0.00444 of beginning assets, compared with 0.00025 for profit, a ratio of approximately 18 to one. In the modified-Jones pooled post-audit-reference sample, mean absolute discretionary accruals decline from 0.0928 to 0.0879, while the median reduction is zero and the interquartile range includes both deterioration and improvement. The mean CFO allocation is positive, whereas the mean PAT and residual benchmark allocations are slightly negative.

\begin{table}[htbp]
\centering
\caption{Descriptive statistics}
\label{tab:descriptive_statistics}
\scriptsize
\resizebox{\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
Variable & $N$ & Mean & SD & P25 & Median & P75 \\
\midrule
\multicolumn{7}{l}{\textit{Panel A: Complete direct-comparison sample}} \\
$\ln(A_{t-1})$ & 8,461 & 27.4663 & 1.5007 & 26.4666 & 27.3442 & 28.3134 \\
$PAT^{pre}/A_{t-1}$ & 8,461 & 0.0528 & 0.1604 & 0.0091 & 0.0402 & 0.0884 \\
$PAT^{post}/A_{t-1}$ & 8,461 & 0.0511 & 0.1705 & 0.0091 & 0.0407 & 0.0891 \\
$CFO^{pre}/A_{t-1}$ & 8,461 & 0.0535 & 0.5495 & -0.0105 & 0.0516 & 0.1341 \\
$CFO^{post}/A_{t-1}$ & 8,461 & 0.0474 & 0.5291 & -0.0105 & 0.0507 & 0.1296 \\
$|\Delta PAT|$ & 8,461 & 0.0047 & 0.0480 & 0.0000 & 0.0002 & 0.0017 \\
$|\Delta CFO|$ & 8,461 & 0.0392 & 0.1991 & 0.0002 & 0.0044 & 0.0254 \\
\addlinespace
\multicolumn{7}{l}{\textit{Panel B: Modified-Jones pooled post-audit-reference attribution sample}} \\
$DA^{pre}$ & 7,801 & 0.0088 & 0.1360 & -0.0544 & 0.0039 & 0.0654 \\
$DA^{post}$ & 7,801 & 0.0113 & 0.1295 & -0.0506 & 0.0044 & 0.0635 \\
$|DA^{pre}|$ & 7,801 & 0.0928 & 0.0998 & 0.0257 & 0.0601 & 0.1199 \\
$|DA^{post}|$ & 7,801 & 0.0879 & 0.0958 & 0.0244 & 0.0573 & 0.1123 \\
$D$ & 7,801 & 0.0049 & 0.0582 & -0.0038 & 0.0000 & 0.0061 \\
$\phi^{PAT}$ & 7,801 & -0.0010 & 0.0161 & -0.0001 & 0.0000 & 0.0001 \\
$\phi^{CFO}$ & 7,801 & 0.0060 & 0.0617 & -0.0026 & 0.0000 & 0.0055 \\
$\phi^{B}$ & 7,801 & -0.0001 & 0.0197 & 0.0000 & 0.0000 & 0.0000 \\
\bottomrule
\end{tabular}%
}
\begin{minipage}{0.97\textwidth}\footnotesize
\textit{Notes:} Financial variables other than $\ln(A_{t-1})$ are scaled by beginning audited assets. Panel~A uses direct reporting-state values without winsorisation. Panel~B uses the modified-Jones model under the pooled historical architecture and post-audit-reference benchmark. $\phi^{B}$ is the residual benchmark component required for exact three-player reconstruction; it is zero for most observations but remains nonzero when the reported total-accrual movement is not exhausted by the PAT and CFO components. Model inputs and total accruals are winsorised using boundaries estimated only from the corresponding historical audited training pool.
\end{minipage}
\end{table}

Table~\ref{tab:direct_revisions} reports the prespecified threshold sensitivity. At the common one-percent cutoff, CFO is material in 38.5 percent of pairs and profit in 7.3 percent. CFO alone is material in 34.8 percent, compared with 3.6 percent for profit alone. The ordering persists at every neighbouring cutoff. Under the asymmetric classification, 32.0 percent of issuer-years have material CFO differences while profit remains stable; 6.2 percent have non-stable profit while CFO is not material. These are observable reporting-state differences and do not establish that either state is correct.

\begin{table}[htbp]
\centering
\caption{Direct constructed-pre-to-post-audit annual differences}
\label{tab:direct_revisions}
\scriptsize
\resizebox{\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
Cutoff & PAT material & CFO material & CFO only & PAT only & Both & Neither \\
\midrule
0.25\% of assets & 20.3\% & 57.0\% & 43.0\% & 6.3\% & 14.0\% & 36.7\% \\
0.50\% of assets & 12.7\% & 48.6\% & 40.8\% & 4.9\% & 7.8\% & 46.5\% \\
1.00\% of assets & 7.3\% & 38.5\% & 34.8\% & 3.6\% & 3.7\% & 57.9\% \\
2.00\% of assets & 4.1\% & 28.8\% & 27.1\% & 2.5\% & 1.6\% & 68.8\% \\
\addlinespace
\multicolumn{7}{l}{\textit{Asymmetric consequence classification}} \\
\multicolumn{3}{l}{CFO material ($|\Delta CFO|\geq0.01$), PAT stable ($|\Delta PAT|\leq0.005$)} & \multicolumn{4}{r}{32.0\%} \\
\multicolumn{3}{l}{PAT non-stable, CFO non-material} & \multicolumn{4}{r}{6.2\%} \\
\bottomrule
\end{tabular}%
}
\begin{minipage}{0.97\textwidth}\footnotesize
\textit{Notes:} $N=8{,}461$ for every row. Differences are scaled by beginning audited assets. The asymmetric rows apply the conventions prespecified in Section~\ref{subsec:direct_design}.
\end{minipage}
\end{table}

\subsection{RQ1: CFO is the larger attributed component}\label{subsec:results_rq1}

Table~\ref{tab:jones_family_attribution} reports the pooled post-audit-reference results. Across all four model families, the median absolute-component contrast is approximately 0.0026 of beginning assets, and every issuer-cluster bootstrap interval excludes zero. CFO is the larger absolute Shapley component in 69.0 percent of issuer-years, with lower confidence bounds above 67 percent. For the two confirmatory Jones-family specifications, mean $D$ is 0.0051 under Jones and 0.0049 under modified Jones; the corresponding one-percent trimmed means are 0.0043 and 0.0042. The confirmatory inference is based on the paired median contrast $|\phi^{CFO}|-|\phi^{PAT}|$, not on these mean reductions.

\begin{table}[htbp]
\centering
\caption{Primary three-player component attribution for RQ1}
\label{tab:jones_family_attribution}
\scriptsize
\resizebox{\textwidth}{!}{%
\begin{tabular}{lrrrrrrrrr}
\toprule
Model & $N$ & Mean $D$ & Trimmed mean $D$ & Mean $\phi^{PAT}$ & Mean $\phi^{CFO}$ & Mean $\phi^{B}$ & Median contrast [95\% CI] & CFO larger [95\% CI] & Normalised median \\
\midrule
Jones & 7,801 & 0.00506 & 0.00429 & -0.00091 & 0.00607 & -0.00011 & 0.00262 [0.00211, 0.00310] & 69.0\% [67.2, 70.7] & 0.0204 \\
Modified Jones & 7,801 & 0.00489 & 0.00419 & -0.00096 & 0.00595 & -0.00010 & 0.00264 [0.00209, 0.00311] & 69.0\% [67.2, 70.6] & 0.0202 \\
Kothari-style ROA-adjusted & 7,801 & 0.00596 & 0.00511 & -0.00001 & 0.00612 & -0.00015 & 0.00262 [0.00207, 0.00319] & 69.0\% [67.3, 70.7] & 0.0212 \\
Nonlinear modified Jones & 7,801 & 0.00601 & 0.00519 & 0.00022 & 0.00593 & -0.00015 & 0.00259 [0.00207, 0.00311] & 69.0\% [67.3, 70.6] & 0.0211 \\
\bottomrule
\end{tabular}%
}
\begin{minipage}{0.97\textwidth}\footnotesize
\textit{Notes:} The contrast is $|\phi^{CFO}|-|\phi^{PAT}|$. $\phi^{B}$ denotes the residual benchmark component in the locked three-player Shapley estimand. Brackets report 2,000-draw issuer-cluster bootstrap percentile intervals. The normalised median divides the observation-level contrast by the historical residual SD for the corresponding model and test year.
\end{minipage}
\end{table}

The signed allocations qualify the absolute-dominance result. Under modified Jones, both PAT and CFO components reduce absolute discretionary accruals in 39.7 percent of observations. CFO reduces absolute discretionary accruals while PAT increases them in 21.1 percent; PAT reduces them while CFO increases them in 23.9 percent; both increase absolute discretionary accruals in 15.3 percent. CFO dominance therefore does not imply that all components move toward a common lower-abnormality state.

The result is stable across the prespecified architecture and reference-state checks. Table~\ref{tab:architecture_sensitivity} shows that the median contrast remains between 0.00258 and 0.00266 across pooled, ICB-industry fixed-effect, industry-specific-slope, and trailing-five-year architectures. The CFO-larger share remains approximately 69 percent throughout. Industry-specific slopes retain 7,666 attribution observations because historical industry cells below the 40-observation minimum are excluded.

\begin{table}[htbp]
\centering
\caption{RQ1 architecture and reference-state sensitivity}
\label{tab:architecture_sensitivity}
\scriptsize
\resizebox{\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
Model & Pooled post ref. & Industry FE & Industry slopes & Trailing five-year & Pooled pre ref. & CFO-larger range \\
\midrule
Jones & 0.002621 & 0.002639 & 0.002599 & 0.002617 & 0.002645 & 68.98--69.04\% \\
Modified Jones & 0.002642 & 0.002657 & 0.002620 & 0.002641 & 0.002643 & 68.98--69.05\% \\
Kothari-style ROA-adjusted & 0.002624 & 0.002618 & 0.002610 & 0.002621 & 0.002649 & 68.98--69.05\% \\
Nonlinear modified Jones & 0.002593 & 0.002613 & 0.002580 & 0.002593 & 0.002605 & 68.98--69.08\% \\
\bottomrule
\end{tabular}%
}
\begin{minipage}{0.97\textwidth}\footnotesize
\textit{Notes:} Entries are median absolute-component contrasts. All issuer-cluster bootstrap intervals exclude zero. Post ref. and pre ref. denote post-audit-reference and pre-audit-reference benchmarks. Industry slopes use ICB Level-1 groups and exclude historical cells below the prespecified minimum.
\end{minipage}
\end{table}

The highest pre-audit-$|DA|$ decile is not necessary for the component-dominance conclusion. Excluding that decile leaves a Jones median contrast of 0.00222 (95-percent CI: 0.00185--0.00273) and a modified-Jones median of 0.00223 (95-percent CI: 0.00180--0.00279). The corresponding CFO-larger shares are 68.5 and 68.4 percent. By contrast, mean $D$ is negative in the first six pre-audit-$|DA|$ deciles and positive in the upper four. Positive average abnormality reduction is therefore tail-concentrated even though the relative component ordering is broad.

Table~\ref{tab:component_time_shift} reports the contemporaneous-pairing diagnostics. Realised medians exceed simulated medians by only $2.5\times10^{-5}$ to $3.3\times10^{-5}$ of beginning assets. None of the six Monte Carlo probabilities is below 0.10. The time-shift designs therefore do not establish that contemporaneous pairing is uniquely informative. This is a boundary on interpretation rather than a rejection of the primary attribution result: CFO remains the larger observed component, but similar median contrasts can arise after breaking the contemporaneous donor pairing.

\begin{table}[htbp]
\centering
\caption{Median time-shift diagnostics for RQ1}
\label{tab:component_time_shift}
\scriptsize
\resizebox{\textwidth}{!}{%
\begin{tabular}{llrrrrr}
\toprule
Model & Donor design & $N$ & Realised median & Simulated median [95\% interval] & Realised minus simulated & $p_{MC}$ \\
\midrule
Jones & Cyclic within issuer & 7,767 & 0.002646 & 0.002618 [0.002578, 0.002668] & 0.000028 & 0.165 \\
Jones & Independent within issuer & 7,767 & 0.002646 & 0.002617 [0.002330, 0.002848] & 0.000030 & 0.437 \\
Jones & Same year/industry peer & 7,767 & 0.002646 & 0.002621 [0.002293, 0.002909] & 0.000025 & 0.454 \\
Modified Jones & Cyclic within issuer & 7,767 & 0.002657 & 0.002624 [0.002581, 0.002672] & 0.000033 & 0.105 \\
Modified Jones & Independent within issuer & 7,767 & 0.002657 & 0.002624 [0.002332, 0.002849] & 0.000033 & 0.415 \\
Modified Jones & Same year/industry peer & 7,767 & 0.002657 & 0.002624 [0.002285, 0.002909] & 0.000033 & 0.428 \\
\bottomrule
\end{tabular}%
}
\begin{minipage}{0.97\textwidth}\footnotesize
\textit{Notes:} Each design uses 2,000 draws. The statistic is the realised median $|\phi^{CFO}|-|\phi^{PAT}|$ minus the simulated median. The benchmark breaks contemporaneous pairing but does not identify a correct reporting state.
\end{minipage}
\end{table}
