\textit{Notes:} Entries for the two benchmarks are simulation means with 2.5th and 97.5th percentiles in brackets. The symmetric-sign benchmark holds the pre-audit value and absolute observed shift fixed and independently assigns the shift direction. The reassignment benchmark permutes observed signed shifts within fiscal year and, for DA, within model--fiscal-year cells. Each benchmark uses 2,000 draws and seed 20260723. Monte Carlo probabilities count ties as exceedances and use the plus-one correction in Equation~\eqref{eq:mc_pvalue}.
\end{minipage}
\end{table}
\subsection{Applied empirical conclusions change selectively}\label{subsec:results_conclusion_sensitivity}

To assess whether the decision-rule instability documented in RQ2 alters familiar archival conclusions, we re-estimate the prespecified conditional associations under both reporting states. None of the 12 continuous-outcome model--design pairs changes five-percent significance status or has a significant state interaction, although two coefficients change sign. The revised reporting hierarchy treats coefficient differences, their intervals, stacked-state interactions, and standardised magnitude changes as primary descriptive outputs; significance-status switching remains a secondary decision-rule illustration.

Standardised changes, paired-difference estimates from Equation~\eqref{eq:paired_difference_regression}, and within-family Benjamini--Hochberg $q$-values are pending rerun in Table~\ref{tab:protocol_extension_outputs}. Classification outcomes are more sensitive. Under modified Jones, the loss--high-$|DA|$ coefficient changes from 0.0213 ($p=0.174$) to 0.0415 ($p=0.007$), with an interaction of 0.0202 ($p=0.027$). Across model families, one classification coefficient changes significance status and two of 24 state interactions are significant. The within-family Benjamini--Hochberg results, rather than a nominal-count heuristic, determine whether this pattern survives multiplicity adjustment; those $q$-values are generated by the completion pipeline. The second interaction occurs in the Jones short-term-debt design: both coefficients remain significant, but the post-audit-state coefficient is 0.0469 lower ($p=0.012$). The consequence is selective, not universal, and concerns conditional associations rather than causal effects.

\begin{table}[htbp]
\centering
\caption{Sensitivity of illustrative conditional associations under the modified-Jones model}
\label{tab:research_conclusion_sensitivity}
\small
\resizebox{\textwidth}{!}{%
\begin{tabular}{lrrrl}
\toprule
Design & Pre-audit coefficient ($p$) & Post-audit coefficient ($p$) & Post-audit--pre-audit interaction ($p$) & Conclusion change \\
\midrule
Big Four and absolute $DA$ & $-0.0010$ (0.909) & 0.0022 (0.813) & 0.0032 (0.264) & No 5\% significance-status change \\
Short-term debt and signed $DA$ & 0.1667 (0.049) & 0.1587 (0.022) & $-0.0080$ (0.901) & No 5\% significance-status change \\
Loss and signed $DA$ & 0.0200 (0.629) & $-0.0072$ (0.859) & $-0.0272$ (0.052) & No 5\% significance-status change \\
Big Four and high-$|DA|$ & 0.0041 (0.713) & 0.0033 (0.750) & $-0.0007$ (0.908) & No 5\% significance-status change \\
Short-term debt and high-$|DA|$ & 0.2951 ($<0.001$) & 0.2719 ($<0.001$) & $-0.0232$ (0.246) & No 5\% significance-status change \\
Loss and high-$|DA|$ & 0.0213 (0.174) & 0.0415 (0.007) & 0.0202 (0.027) & Significance status changes \\
\bottomrule
\end{tabular}%
}
\begin{minipage}{0.97\textwidth}\footnotesize
\textit{Notes:} Each specification uses 7,789 issuer-years and 1,015 issuers. All explanatory variables are fixed at constructed pre-audit annual values. Models include log beginning assets, constructed pre-audit ROA, current ratio, short-term-debt intensity, loss status, Big Four status, fiscal-year fixed effects, and ICB-industry fixed effects, excluding the focal variable from the remaining controls. Continuous covariates are winsorised at the first and ninety-ninth percentiles within model. Separate-state and stacked interaction specifications follow Equations~\eqref{eq:separate_state_regression} and~\eqref{eq:stacked_state_regression}; repeated state observations and standard errors are clustered by issuer. High-$|DA|$ models are linear-probability models using the common contemporaneous post-audit-state ninetieth-percentile boundary defined in Section~\ref{subsec:switching_design}.
\end{minipage}
\end{table}
\subsection{Statement-level patterns do not identify a unique mechanism}\label{subsec:results_channels}

Offset shares are available for 7,155 locked observations, of which 1,265 meet the identity-conditioned candidate rule. Investing offsets dominate more often when post-audit CFO increases; financing offsets dominate more often when post-audit CFO decreases. The mapped analysis retains 1,046 observations. Its uncapped ratio has a mean of 1.312 and a median of 1.055, and the bounded ratio is capped in 82.2 percent. Observed concentration is below its firm-year allocation benchmark (mean excess $NHHI=-0.187$). The benchmark holds each firm-year's revision magnitude and active line-item structure fixed while reallocating the movement according to observed transaction weights. Using the uncapped mapping ratio as the primary specification, the mapping-intensity coefficient is 0.00382 ($p=0.299$) after controlling for largest-concept dominance; the heavily saturated bounded ratio is descriptive only. A deterministic reversal sets median $D$ to zero in low-profit-change mapped cases, reproducing the accrual identity without identifying why the movement occurred.

The near-zero diagnostic is also unstable. Estimates are negative around zero, but placebo cutoffs produce opposite signs; the 75th-percentile placebo estimate (0.604) exceeds the zero-centred estimates in magnitude (Table~\ref{tab:near_zero_sensitivity}). The random-sign benchmark remains compatible with the observed asymmetry. The prior preparation-friction implementation contained only nine positive incompleteness cases, but it did not cleanly separate the complete-primitives mapping population from the broader otherwise-eligible preparation population. The revised indicator requires a pre-audit-state primitive to be missing and the corresponding post-audit primitive to be available or reconcilable; its eligible population, positive count, and regression estimates are pending rerun. These diagnostics restrict mechanism claims rather than alter the RQ results.

\begin{table}[htbp]
\centering
\caption{Near-zero-CFO directional-diagnostic sensitivity}
\label{tab:near_zero_sensitivity}
\small
\begin{tabular}{p{0.48\textwidth}rrr}
\toprule
Specification & Centre / cutoff & $N$ & Crossing asymmetry \\
\midrule
0.5-percent window around CFO zero & 0.0000 & 37 & $-0.530$ \\
1-percent window around CFO zero & 0.0000 & 69 & $-0.357$ \\
2-percent window around CFO zero & 0.0000 & 135 & $-0.390$ \\
Placebo cutoff: CFO distribution 25th percentile & $-0.0473$ & 48 & $-0.433$ \\
Placebo cutoff: CFO distribution 75th percentile & 0.1781 & 41 & 0.604 \\
Alternative deflator: constructed pre-audit revenue & 0.0000 & 60 & $-0.141$ \\
\bottomrule
\end{tabular}
\begin{minipage}{0.94\textwidth}\footnotesize
\textit{Notes:} Crossing asymmetry is the below-to-above crossing rate minus the above-to-below crossing rate within the relevant matched-distance sample. The first three rows vary the CFO/assets window around zero. The placebo rows apply the same design around empirical CFO cutoffs without institutional significance. The final row replaces beginning assets with constructed pre-audit revenue as the deflator.
\end{minipage}
\end{table}

\subsection{Protocol-extension outputs required by the revised design}\label{subsec:results_pending}

Table~\ref{tab:protocol_extension_outputs} identifies the outputs added by the revised research design. They require a pipeline rerun and are intentionally left unreported rather than reconstructed from aggregate tables. Existing point estimates remain visible above so that changes produced by the rerun can be reconciled transparently.

\begin{table}[htbp]
\centering
\caption{Protocol-extension outputs pending pipeline rerun}
\label{tab:protocol_extension_outputs}
\small
\begin{tabular}{p{0.46\textwidth}p{0.34\textwidth}p{0.12\textwidth}}
\toprule
Required output & Reporting location after rerun & Status \\
\midrule
Neighbouring direct-difference threshold counts (0.25\%, 0.50\%, 1.00\%, 2.00\% of assets) & Sample and direct differences & Pending \\
Industry-FE, industry-specific-slope, trailing-five-year, and zero-dispersion accrual-model checks & RQ1 architecture sensitivity & Pending \\
Historical-residual-scale-normalised component contrasts and CFO-dominant shares & RQ1 component attribution & Pending \\
Signed Shapley quadrants and signed residual-movement directions & RQ1 component attribution & Pending \\
Issuer-cluster bootstrap interval for CFO-larger share & RQ1 component attribution & Pending \\
Median-based within-firm time-shift statistic, interval, and Monte Carlo $p$ & RQ1 validation & Pending \\
Independent within-issuer and same-year/industry cross-issuer donor sensitivities & RQ1 validation & Pending \\
Midrank common post-audit CDF ranks and common-boundary CFO-category switch outputs & RQ2 switching and coverage & Pending \\
Issuer-cluster bootstrap intervals for each switch rate and outside-gate share & RQ2 switching and coverage & Pending \\
Year-specific Jaccard indices and pooled-versus-year sensitivity & RQ2 switching and coverage & Pending \\
Monte Carlo $p$-values for all symmetric-sign and signed-shift benchmarks & Randomisation benchmarks & Pending \\
Coefficient changes standardised by common-sample pre-audit outcome SD, coefficient-difference intervals, and paired-difference regressions & Applied-consequence tests & Pending \\
Revised preparation-friction population, positive count, and regressions & Supplemental diagnostics & Pending \\
Holm-adjusted primary composite-rule probabilities and Benjamini--Hochberg secondary-family $q$-values & Confirmatory and secondary inference & Pending \\
Centred cluster-bootstrap directional probabilities & RQ1 and RQ2 criteria & Pending \\
Test-specific missing-data denominators and exclusions manifest & All results tables & Pending \\
\bottomrule
\end{tabular}
\end{table}
